MS_Imp_Guidelines

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Available_Data_And_Resources.Rmd
working on discussion
cull

Development versions of all code repositories referenced in this article are available in https://github.com/ready4-dev/ . Archived code releases are available in https://zenodo.org/communities/ready4  .

All data repositories referenced in this article are available in https://dataverse.harvard.edu/dataverse/ready4 .

>>>>

The ready4 framework is documented at https://www.ready4-dev.com. Documentation on readyforwhatsnext is available at https://readyforwhatsnext.org/. Development versions of all code repositories referenced in this article are available in https://github.com/ready4-dev/. Archived code releases are available in https://zenodo.org/communities/ready4. All data repositories referenced in this article are available in https://dataverse.harvard.edu/dataverse/ready4.

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
cull

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
<!-- We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria.  -->
We have developed a prototype software framework that can support the implementation of CHEMs that largely meet explicit criteria for CHEM transparency, reusability and updataility. Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs. Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders.

>>>>

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
<!-- We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria.  -->
Our software framework provides the outline of a technical solution to some of the challenges of transferable CHEM development using open-source and modular approaches. Our framework can be used as a prototype for developing future software frameworks to support implementation of transferable CHEMs. 
<!-- Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders. -->

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
cull

As illustrated by Table \@ref(tab:checktb), we have developed a prototype software framework that can be used to implement youth mental health CHEMs that largely satisfy our TRU criteria. However, in its current form our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects. We developed our prototype software framework primarily to address the user requirements of one group – ourselves. Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development]. We currently lack the resources required to  address these issues for our software framework.

However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate. Firstly, developing a software framework to work within an existing and widely used open source programming language such as R, can keep framework scope relatively narrow. This makes it more tractable to develop, maintain and learn, and facilitates integration with other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)). Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts. Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation [@beck2001manifesto]). Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update. All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently. Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code and documentation authoring capabilities of large language models.

Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development. However, better tools alone are insufficient and policy and institutional changes are also required. <!-- Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful. Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model. Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment]. Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019]. Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies. --> A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions. Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

>>>>

As illustrated by Table \@ref(tab:checktb), we have developed a software framework and used it to implement CHEM modules that largely satisfy explicit criteria for transparency, reusability and updatability. However, in its current status as a development release, our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects. <!-- We developed our prototype software framework primarily to address the user requirements of one group – ourselves.  -->Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development]. We currently lack the resources required to systematically address these issues for our software framework.

However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate. Firstly, developing a software framework to work within an existing and widely used open source programming language such as R, can keep framework scope relatively narrow. This makes it more tractable to develop, maintain and learn, and facilitates integration with other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)). Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts. Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and prioritising the development of working code over writing documentation  (a foundation principle of Agile Software Development [@beck2001manifesto]). Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update. All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently. Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code and documentation authoring capabilities of large language models.

We have used toy data to demonstrate how our initial readyforwhatsnext CHEM module libraries, originally developed for a single utility mapping study [@Hamilton2021.07.07.21260129], can be applied to datasets with different concepts and variable names, to construct models with different utility instruments, predictors and covariates and to develop and use both cross-sectional and longitudinal mapping models. However, it should be noted that these CHEM module libraries are currently only available as development releases. When assessing libraries against TRU criteria, we identified the need to write more custom documentation and unit tests of individual modules. We plan to undertake these improvements as part of future quality assurance work required prior to submission of these libraries for archiving on CRAN [@CRAN2022].

It is also important to highlight that our framework only addresses barriers to health economic model transferability that arise from how a model is implemented as software (ie, CHEMs). Health economists must also consider conceptual or theoretical validity issues. For example, the candidate models currently available in our scorz library [@hamilton_matthew_2022_6084824] were chosen because of their suitability for mapping to the utility instrument (AQoL-6D [@Richardson2012AQ]) used in the study [@Hamilton2021.07.07.21260129] for which scorz was originally developed. It is likely that other types of model would be more appropriate for mapping to utility instruments that produce less continuous total score distributions [@Hamilton2021.07.07.21260129]. Therefore, although the utility mapping modules of readyforwhatsnext *can* be used to develop models to map to different utility instruments, further development of these tools will be required before *validly applied* to some study questions. Our software framework is designed to make such required extensions more straightforward to implement.

Greater use of reference models [@Afzali2013], methodological innovation to improve model transferability [@craig2018taking] and the development of regularly updated CHEMs that can support "living Health Technology Assessment" [@thokala2023living] have all previously been recommended. Software frameworks could be enabling technologies for all of these goals. <!-- However, better tools alone are insufficient and policy and institutional changes are also required.  -->
<!-- Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful. Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model. Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment]. Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019]. Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies. --> A future software framework for transferable CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions. Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
cull

## Model user requirements
The initial model user requirements (MURs) that we specified for the readyforwhatsnext modules we developed for utility mapping are:

MUR 1) *Variable validation tools* that: (i) define the allowable range (minimum and maximum) and numeric class (integer or double precision) associated with different psychological, functional and health utility summary measures appropriate for use in youth mental health samples; (ii) provide an informative error message that halts an analysis or reporting program's execution should impermissible values be assigned to each measure.

MUR 2) *Dataset description tools* that: (i) attach structured metadata to a human records dataset that specify the unique person identifier, group assignment and data collection round variables; and (ii) generate tabular and graphical summaries of dataset descriptive statistics.

MUR 3) *Multi-attribute instrument scoring tools* that: (i) attach structured metadata about an instrument (e.g. name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) apply pre-written (for AQol-6D and EQ-5D instruments) or user-supplied instrument scoring functions to a human records dataset; and (iii) generate descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).

@@

MUR 5) *Utility mapping study reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific summary manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a single consolidated study reproducibility program that implements all steps inclusive of data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.

MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhastnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) applies selected utility mapping model to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).

@@

### Modules
We used all six ready4 framework libraries to author five development version readyforwhatsnext module libraries (Table \@ref(tab:rfwnlibs)). These libraries are youthvars [@hamilton_matthew_2022_6084467] which addresses MURs 1 and 2, scorz [@hamilton_matthew_2022_6084824] which addresses MUR 3, specific [@hamilton_matthew_2022_6116701] which addresses MUR 4, TTU [@gao_caroline_2022_6130155] which addresses MUR 5 and youthu [@matthew_p_hamilton_2021_5646669] which addresses MUR 6.

### Reporting templates
We used the framework reporting tools library to author two reporting templates that are designed to be used in conjunction with these utility mapping models. The first reporting template is used to create a catalogue of utility mapping models [@hamilton_matthew_2022_6116385]. The second reporting template can be used to generate a manuscript [@matthew_p_hamilton_2022_5976988] providing a scientific summary of each study implemented with these modules.

### Application
We have previously described a study [@Hamilton2021.07.07.21260129] that used applied these modules and reporting templates to develop utility mapping models in a sample of young people presenting to primary mental health services. We used these module libraries to write programs that reproduced that study's reporting and analysis algorithm [@hamilton_matthew_2022_6129906], to demonstrate how to applying the utility mapping models constructed in that study to new data [@hamilton_matthew_2022_6416330] and to generate a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821]. We also created an open access study input parameters and results dataset [@DVN/DKDIB0_2021]) and toy datasets to help demonstrate the transferability of the study algorithm [@DVN/HJXYKQ_2021]).

@@

## Documentation website
We used using the search and documentation tools from our foundation framework library to
create and help maintain a documentation website (https://readyforwhatsnext.org/) that includes details on available model modules, datasets and analysis programs and tutorials on using model modules.

## Transferability assessment
We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->our TRU criteria <!-- Edit_end --> (Table \@ref(tab:checktb)). For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.  We believe our utility mapping study modules have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2). The main shortcomings that we identified when applying the assessment criteria was that we have yet to: (i) ensure that module library documentation includes examples of how to apply all exported methods and functions; and (ii) adequately implement unit testing.

>>>>

## Model user requirements
The model user requirements (MURs) that we specified for the readyforwhatsnext's initial modules are:

MUR 1) *Variable validation tools* that: (i) define the allowable values and numeric class (integer or double precision) associated with different psychological, functional and health utility measures appropriate for use in youth mental health samples; (ii) provide an informative error message that halts an analysis or reporting program's execution should impermissible values be assigned to each measure.

MUR 2) *Dataset description tools* that: (i) attach structured metadata to a human records dataset that specify unique person identifier, group assignment and data collection round variables; and (ii) generate tabular and graphical summaries of dataset descriptive statistics.

MUR 3) *Multi-attribute instrument scoring tools* that: (i) attach structured metadata about an instrument (e.g. name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) apply pre-written (for AQol-6D [@Richardson2012AQ] and EQ-5D [@devlin2017eq] instruments) or user-supplied instrument scoring functions to a human records dataset; and (iii) generate descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).

@@

MUR 5) *Utility mapping study reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a consolidated study replication program that implements data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.

MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhastnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) apply selected utility mapping models to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).

@@

### Module libraries
We used all six ready4 framework libraries to author five development version readyforwhatsnext module libraries (Table \@ref(tab:rfwnlibs)). These libraries are youthvars [@hamilton_matthew_2022_6084467] which addresses MURs 1 and 2, scorz [@hamilton_matthew_2022_6084824] which addresses MUR 3, specific [@hamilton_matthew_2022_6116701] which addresses MUR 4, TTU [@gao_caroline_2022_6130155] which addresses MUR 5 and youthu [@matthew_p_hamilton_2021_5646669] which addresses MUR 6.

### Reporting templates
We used the framework reporting tools library to author two reporting templates that are designed to be used in conjunction with these utility mapping modules. The first reporting template [@hamilton_matthew_2022_6116385] is used to create a catalogue of utility mapping models. The second reporting template [@matthew_p_hamilton_2022_5976988] can be used to generate a manuscript providing a scientific summary of each study implemented with these modules.

### Application
We have previously described a study [@Hamilton2021.07.07.21260129] that used these module libraries and reporting templates to develop and document utility mapping models in a sample of young people presenting to primary mental health services. We used these module libraries to write programs for replicating that study's reporting and analysis algorithm [@hamilton_matthew_2022_6129906], to demonstrate how to apply the utility mapping models constructed in that study to new data [@hamilton_matthew_2022_6416330] and to generate a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821]. We also created an open access study input parameters and results dataset [@DVN/DKDIB0_2021] and toy datasets to help demonstrate the transferability of the study algorithm [@DVN/HJXYKQ_2021].

@@

## Documentation website
Using the framework website as a template, we used the search and documentation tools from our foundation framework library to create and help maintain a project documentation website (https://readyforwhatsnext.org/). The project website includes details on available model modules, datasets and analysis programs and tutorials on how these artefacts can be used.

## Transferability assessment
We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->TRU criteria <!-- Edit_end --> (Table \@ref(tab:checktb)). For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”. We believe that our utility mapping study module libraries, code and data repositories and documentation have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2). The main shortcomings that we identified when applying the assessment criteria was that individual modules and functions have yet to: (i) be supported with human authored documentation that includes examples of how they can be used; and (ii) be quality assured through unit testing.

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
abstract updated
cull

We became interested in solving some of the technical barriers to transferable CHEMs in 2018 when considering how to synthesise multiple youth mental health economic modelling projectsin one multi-purpose model. This overarching youth mental health model is called readyforwhatsnext [@rfwn2024].

@@

Potential future directions for readyforwhatsnext may incorporate projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce). Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in two additional Wagstaff and Culyer domains:

@@

However, there are ethical risks associated with each potential transfer, in particular the need to ensure the social acceptability, fitness for purpose and appropriate use of readyforwhatsnext in each new decision context [@ethicsCHEMS2024]. For that reason, we have set the goal of readyforwhatsnext meeting six explicit criteria for transparency, reusability and updatability (TRU criteria). We have describe these criteria and their origins in ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:

@@

T2) Developer contributions are easily identified;

@@

U6) Software is systematically retested and deprecated.

We are developing readyforwhatsnext using real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets. Toy data created for illustration purposes is prominently labelled as not for use in decision-analysis.
<!-- PHNS -->
A high level schematic guiding our implementation of readyforwhatsnext as a transferable CHEM is outlined in Figure \@ref(fig:fig1).

>>>>

We became interested in solving some of the technical barriers to transferable CHEMs in 2018 when considering how to synthesise multiple youth mental health economic modelling projects in one multi-purpose model. This overarching youth mental health model is called readyforwhatsnext [@rfwn2024].

@@

Potential future directions for readyforwhatsnext may incorporate projects in two additional domains: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce). Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in a further two domains:

@@

However, there are ethical risks associated with each potential transfer, in particular the need to ensure the social acceptability, fitness for purpose and appropriate use of a CHEM in each new decision context [@ethicsCHEMS2024]. For that reason, we have set the goal of readyforwhatsnext meeting six explicit criteria for transparency, reusability and updatability (TRU criteria). We have described these criteria and their origins in ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:

@@

T2) Developer contributions and judgments on appropriate use are easily identified;

@@

U6) Releases are systematically retested and deprecated.

To achieve these goals we are implementing readyforwhatsnext as an open-source, modular model. Open source projects grant third parties liberal permissions to access, use and modify model source code and data. A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. <!-- Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. -->We are developing readyforwhatsnext using real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets. Toy data created for illustration purposes is prominently labelled as not for use in decision-analysis.
<!-- PHNS -->
A high level schematic guiding our implementation of readyforwhatsnext as a transferable CHEM is outlined in Figure \@ref(fig:fig1).

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
cull

FUR 3) *Module authoring tools* that integrate with online software development services to help author R libraries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled with authorship, funding source, version number and a Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.

@@

FUR 5) *Reporting tools* that: help (i) author reporting templates that render documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting templates  from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting templates to render reports and scientific summaries.
<!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->

@@

FUR 7) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a project documentation website that consolidates content from the websites of individual module libraries, datasets and programs; and (ii) partially automate the updating of website resources such as tutorials and itemised lists of code and data releases.

@@

One library provides the foundation for the ready4 framework. <!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].  -->The ready4 foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm. Two notable features of object-oriented programming are encapsulation [@8717448] and inheritence [@8717448]. Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when combined<!-- [@ready4oop2022] -->. Inheritence allows new CHEM modules to inherit some or all of the properties of a parent module. Inheritence is useful when it is necessary to selectively modify CHEM modules, for example to that to account for interaction effects when CHEMs are combined or to account for the features of a different decision contexts to which they are being transferred<!-- [@ready4oop2022] -->. The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties (meeting *FUR 1*). One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *FUR 2*). The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *FUR 6*) and tools for developing and maintaining a project documentation website (*FUR 7*).

Three framework module authoring libraries are designed to meet *FUR 3*. <!-- Define functional and object-oriented approaches, acceptance and unit testing. -->The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452]. Authoring with each of these paradigms is supported by ready4. One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function. A second module authoring library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module. A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are: documented (with a website and PDF manuals); licensed (using the copyleft GNU GPL-3 [66] by default); easily citable (citation information can be retrieved within an R session or from hosting repositories); and quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).

A library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *FUR 4*). A library for authoring reproducible analysis programs and reporting subroutines (*FUR5*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses. The library supports the creation of analysis programs that are self-documenting (code is integrated with plain English explanations of what it does) and subroutines that can be used as templates that trigger the creation of explanatory documents (e.g., a scientific manuscript).

@@

###	Online services 
Framework libraries are designed to be used in conjunction with a number of third-party online services that developers using ready4 need to establish and configure accounts with. The framework's module authoring tools integrate with online code development, testing and archiving services. The ready4 framework uses the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions. The continuous integration [@CI2017] tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit. <!-- Imported -->These tests can be unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]). A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - reports of the proportion of code that has been explicitly tested. The ready4 framework uses the codecov [@codecov_2022] service to measure and share information about code coverage. <!-- End_Imported -->The open science repository service Zenodo [@Zenodo2013] is used to provide persistent storage, uniquely identified with a a Digital Object Identifier (DOI), of each code release. The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data. For the management of frequently updated datasets that do not require persistent storage, ready4 uses GitHub.

>>>>

FUR 3) *Module authoring tools* that integrate with online software development services to help author R libraries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled with authorship, funding source, version number and Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.

@@

FUR 5) *Reporting tools* that: help (i) author reporting templates for rendering documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting templates from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting templates to render custom reports and scientific summaries.
<!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->

@@

FUR 7) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a CHEM project documentation website that consolidates content from the websites of individual CHEM module libraries, datasets and programs; and (ii) partially automate the updating of website resources such as tutorials and itemised lists of code and data releases.

@@

One library provides the foundation for the ready4 framework. <!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].  -->To meet *FUR 1*, the ready4 [@ready4lib24] foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm. Two notable features of object-oriented programming are encapsulation [@8717448] and inheritance [@8717448]. Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when combined<!-- [@ready4oop2022] -->. Inheritance allows new CHEM modules to inherit some or all of the properties of a parent module. Inheritance is useful when it is necessary to selectively modify CHEM modules, for example to account for: (i) interaction effects when CHEMs are combined; or (ii) distinctive features of a new decision contexts to which they are being transferred<!-- [@ready4oop2022] -->. The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties. One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *FUR 2*). The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *FUR 6*) and tools for developing and maintaining a CHEM project's documentation website (meeting *FUR 7*).

Three framework module authoring libraries are designed to meet *FUR 3*. <!-- Define functional and object-oriented approaches, acceptance and unit testing. -->The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452]. Authoring with each of these paradigms is supported by ready4. The ready4fun [@ready4funlib24] library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function. The ready4class [@ready4classlib24] library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module. The ready4pack [@ready4packlib24] library provides tools for disseminating themed bundles of CHEM modules as R libraries that are: documented (with a website and PDF manuals); licensed (using the copyleft GNU GPL-3 [66] by default); easily citable (citation information can be retrieved within an R session or from hosting repositories); and quality assured (each update triggers the running of any tests created by module library authors, with test results publicly documented).

The ready4use [@ready4uselib24] library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *FUR 4*). The ready4show [@ready4showlib24] library for authoring reproducible analysis programs and reporting subroutines (*FUR5*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking reproducible health economic analyses. The library supports the creation of analysis programs that are self-documenting (code is integrated with plain English explanations of what it does) and subroutines that can be used as templates that trigger the creation of explanatory documents (e.g., a scientific manuscript).

@@

###	Online services 
Framework libraries are designed to be used in conjunction with a number of third-party online services. The framework's module authoring tools use the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions. The continuous integration [@CI2017] tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit. <!-- Imported -->These tests can be unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]). A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - reports of the proportion of code that has been explicitly tested. The module authoring libraries use the codecov [@codecov_2022] service to measure and share information about code coverage. <!-- End_Imported -->The open science repository service Zenodo [@Zenodo2013] is used by the module authoring libraries to provide persistent storage, uniquely identified with a Digital Object Identifier (DOI), of each code release. The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data. For the management of frequently updated datasets that do not require persistent storage, all framework libraries use GitHub.
